Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-03-23 ch04-lrmhinf/paper.tex
small changes ch-2,ch04
Improve bibliography

\TODO{
  \begin{itemize}
    \item fix labels for chapter
    \item add section from Benchmark paper
    \item fix some bib entries
    \item Hinf macro aanpassen voor PDF support (indien dit niet conflicteert met glossaries)
  \end{itemize}
}
\input{\thisDir/styles.inc.tex}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/interpolation-show.tikz}
  \caption[Illustration of the local models.]{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\set{1,\ldots,6}$.
  The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
\label{fig:interpol-quantities}
\end{figure}

@@

Classical \gls{SA} techniques~\citep{Bendat1980} can estimate the \gls{FRF} of $\Delta$.
This is done by first splitting the input/output signals into $N_S$ segments of ${N}/{N_S}$ samples, windowing the segments to reduce leakage and applying the \gls{DFT}.
By dividing the resulting output/input spectra, the \gls{FRF} is obtained.
In this paper a Hann window and $N_S=1$ are used.
Note that $N_S>1$  increases the measurement time by a factor $N_S$ to attain the same frequency resolution (but would improve  transient and noise rejection).

>>>>

  \begin{itemize}
    \item \TODO{fix labels for chapter}
    \item \TODO{add section from Benchmark paper}
    \item \TODO{fix some bib entries}
    \item \TODO{Hinf macro aanpassen voor PDF support (indien dit niet conflicteert met glossaries)}
  \end{itemize}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.68\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/interpolation-show.tikz}
  \caption[Illustration of the local models.]{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\set{1,\ldots,6}$.
  The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
\label{fig:interpol-quantities}
\end{figure}

@@

Classical \gls{SA} techniques~\citep{Bendat1993} can estimate the \gls{FRF} of $\Delta$.
This is done by first splitting the input/output signals into $N_S$ segments of ${N}/{N_S}$ samples, windowing the segments to reduce leakage and applying the \gls{DFT}.
By dividing the resulting output/input spectra, the \gls{FRF} is obtained.
In this paper a Hann window and $N_S=1$ are used.
Note that $N_S>1$  increases the measurement time by a factor $N_S$ to attain the same frequency resolution (but would improve  transient and noise rejection).
